Difficult Text Analysis of Machine Translation Services base on Metamorphic Testing in Social Media

### 2019-01-22 icse/paper.tex
backup

>>>>

\section{Background}
\subsection{Metamorphic Testing}
Metamorphosis Testing(MT) a method for generating test cases, as well as test
results verification. The most importance component is the metamorphic
relation(MR). MR is the target application's necessary properties of function in relation to multiple
inputs and their expected outputs. When people want to assess the
the accuracy of $\sin$ function. For example, $\sin(2.7)$ is very difficult to
make a correctness judgment from mathematics aspect. If using Metamorphic
Testing method to testing $\sin$ function will reduce computational costs and
more efficient.
\begin{enumerate}
\item set a Metamorphic relation: such as $\sin(\alpha) = \cos(\frac{\pi}{2} - \alpha)$
\item

\end{enumerate}
However, when using
Metamorphic Testing method set a metamorphic relation, which is  will less cost . If  make a correctness judgment

which are expected relations among the inputs and
outputs of multiple executions of the intended program’s functionality.

are an approach for generating both test cases and test results. A central element is a set of metamorphosis
relationships, which are necessary properties of the objective function or the algorithm in relation to multiple inputs and their expected
outputs.

Since its first publication, we have witnessed a rapidly increasing body of work examining metamorphic testing from
various perspectives, including metamorphic relation identification, test case generation, integration with other software engineering
techniques, and the validation and evaluation of software systems.

In software testing, an inability to determine if software is behaving
correctly, or producing the correct output, is called the oracle problem [1]. Metamorphic testing (MT) is an approach that can alleviate
the oracle problem [6, 10], MT has been investigated and adopted by
a growing number of researchers and practitioners [7, 16, 20, 21, 28],
successfully uncovering software problems, even in extensively
tested systems [8, 9, 19]. Central to MT is a set of metamorphic
relations (MRs), which are expected relations among the inputs and
outputs of multiple executions of the intended program’s functionality. Instead of examining the behaviour or output for an individual
input, MT checks the SUT against selected MRs, with violations of
an MR indicating the presence of a fault.
An example MR for a database management system is that the
system should return the same results for a query with the search
condition “A and B” and a query with the search condition “B and
A”.
\subsection{Sentiment Analysis}
